Active Learning for Level Set Estimation

### 2013-03-18 msthpres.tex
Extra intro figure; timings; add general problem statement

% $Header: /Users/joseph/Documents/LaTeX/beamer/solutions/conference-talks/conference-ornate-20min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

@@

% This file is a solution template for:

% - Talk at a conference/colloquium.
% - Talk length is about 20min.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

@@

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

@@

\begin{frame}
\begin{center}
Swimmers of Lake Zurich, beware!
\vspace{0.2in}
\begin{columns}[c]
\column{0.4\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
\includegraphics[width=1.7in]{figures/pr.jpeg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}\\
\vfill
\includegraphics[width=1.7in]{figures/bloom.jpg}\\[-0.5em]
{\tiny (Source: Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey)}
\endminipage

\column{0.6\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
{\small
``The warming waters of one of central Europe's most popular holiday
destinations, Switzerland's Lake Zurich, have created an ideal environment
for a population explosion of algae including \emph{Planktothrix rubescens},
[...]''
\qauth{Scientific American}
\vfill

``\emph{Planktotrhix rubescens} can account for half of the total
phytoplankton biomass in Lake Zurich in summer [...]''
\vfill

``\emph{Planktotrhix rubescens} are among the most important
producers of hepatotoxic microcystins in freshwaters [...]''
\qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
\vfill

``Microcystins [...] are cyanotoxins and can be very toxic for plants and
animals including humans.
Their hepatotoxicity may cause serious damage to the liver.''}
\qauth{Wikipedia}
\endminipage
\end{columns}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=2in]{figures/manual.jpg}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/boat.jpg}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/lake.png}\\
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

@@

>>>>

@@

@@

%\pgfdeclareimage[height=0.5cm]{university-logo}{figures/eth_logo_black.pdf}
%\logo{\pgfuseimage{university-logo}}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command: 
%\beamerdefaultoverlayspecification{<+->}

@@

\begin{frame}
\begin{center}
Swimmers of Lake Zurich, beware!\\
\vspace{0.2in}
\includegraphics[width=4in]{figures/swimmers.jpg}\\[-0.5em]
{\tiny (Source: Steffen Schmidt / EPA)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\uncover<1->{Swimmers of Lake Zurich, beware!}
\vspace{0.2in}
\begin{columns}[c]
\column{0.4\textwidth}
\uncover<1->{
\minipage[c][0.75\textheight][s]{\columnwidth}
\includegraphics[width=1.7in]{figures/pr.jpeg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}\\
\vfill
\includegraphics[width=1.7in]{figures/bloom.jpg}\\[-0.5em]
{\tiny (Source: Flickr/Dr. Jennifer L. Graham/U.S. Geological Survey)}
\endminipage
}

\column{0.6\textwidth}
\minipage[c][0.75\textheight][s]{\columnwidth}
\uncover<1->{
\small
``The warming waters of one of central Europe's most popular holiday
destinations, Switzerland's Lake Zurich, have created an ideal environment
for a population explosion of algae including \emph{Planktothrix rubescens},
[...]''
\qauth{Scientific American}
}
\vfill
\uncover<2->{
\small
``\emph{Planktotrhix rubescens} can account for half of the total
phytoplankton biomass in Lake Zurich in summer [...]''
\vspace{1em}

``\emph{Planktotrhix rubescens} are among the most important
producers of hepatotoxic microcystins in freshwaters [...]''
\qauth{Silke Van den Wyngaert \emph{et al.}, ASLO, 2011}
}
\vfill
\uncover<3->{
\small
``Microcystins [...] are cyanotoxins and can be very toxic for plants and
animals including humans.
Their hepatotoxicity may cause serious damage to the liver.''
\qauth{Wikipedia}
}
\endminipage
\end{columns}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=2in]{figures/manual.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/boat.jpg}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\vspace{0.2in}
\includegraphics[width=4in]{figures/lake.png}\\[-0.5em]
{\tiny (Source: www.limnobotics.ch)}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{itemize}
\item<1-> Pose as a sequential decision making problem (\emph{pool-based active learning}):
\begin{itemize}
\item<2-> No measurements available in advance, just a set (pool) of possible sampling locations ($D$)
\vspace{0.5em}
\item<3->[]\hspace{-1.5em} At each iteration $t \geq 1$:
\item<3-> Decide where to measure next ($x_t$)
\item<4-> Obtain noisy observation ($y_t = f(x_t) + n_t$)
\item<5-> Update our estimate of the underlying function (e.g. algae concentration)
\end{itemize}
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1>[draft,width=4.45in]{figures/oned_0}
\color{black}
\includegraphics<2>[width=4.45in]{figures/oned_0}
\includegraphics<3>[width=4.45in]{figures/oned_1_0}
\includegraphics<4>[width=4.45in]{figures/oned_1_1}
\includegraphics<5>[width=4.45in]{figures/oned_1_2}
\includegraphics<6>[width=4.45in]{figures/oned_2_0}
\includegraphics<7>[width=4.45in]{figures/oned_2_1}
\includegraphics<8>[width=4.45in]{figures/oned_2_2}
\end{center}
\end{frame}

\begin{frame}
\begin{enumerate}
\item<1-> How do we \textbf{model} the function?
\vspace{1em}
\item<2-> How do we \textbf{classify}?
\vspace{1em}
\item<3-> Each measurement is expensive (time, battery power).\\
      How do we \textbf{select} ``informative'' measurements?
\end{enumerate}
\vspace{2em}
\begin{center}
\uncover<4->{\large
Gaussian processes to the rescue!
}
\end{center}
\end{frame}
